MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-12-29 article/main.tex
Closes #1

Neff introduced the notion of verifiable shuffle \cite{neff2001verifiable}. It is a cryptographic protocol allowing a party to verifiably shuffle a sequence of $k$ modular integers. The output of the shuffle is another $k$ modular integers raised to the same secret exponent only known to the shuffler. The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly.

>>>>

Neff introduced the notion of verifiable shuffle \cite{neff2001verifiable}. It is a cryptographic protocol allowing a party to verifiably shuffle a sequence of $k$ modular integers. The output of the shuffle is another $k$ modular integers multiplied by the same secret multiplier only known to the shuffler. The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly without disclosing the secret multiplier.
